An event-sourced and decentralized database with IPLD and materialized views

### 2019-09-22 draft.tex

Much like IPFS Peers, Logs are identified on the network with addresses, or more specifically, with multiaddresses [ref]. Here we introduce IPEL, or Interplanetary Event Log, as a new protocol tag to be used when composing Log multiaddresses (Example \ref{ex:Multiaddress}).

>>>>

Much like IPFS Peers, Logs are identified on the network with addresses, or more specifically, with multiaddresses\cite{Multiaddr}. Here we introduce IPEL, or Interplanetary Event Log, as a new protocol tag to be used when composing Log multiaddresses. To reach a Log via it's IPEL multiaddress, it must be encapsulated in an IPFS Peer multiaddress (see Example \ref{ex:Multiaddress}).
